$\epsilon$-explicit analysis of DPG for convection-dominated diffusion

### 2012-04-06 docs/NewBCRobustness_paper/paper.tex
added density argument
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@450 36274a68-8941-4c93-80ef-affaed5139da

\author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
\title{$\epsilon$-explicit analysis of DPG}
\date{}
\begin{document}

@@

We reduce the adjoint problem to the scalar second order equation
\begin{equation}
- \epsilon \Delta v - \beta \cdot \grad v = g - \epsilon \div f \label{adjoint}
\end{equation}
with boundary conditions
\begin{align}
%\tau \cdot n = 
- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{reducedbc_1}\\ 
v &= 0, \quad x\in \Gamma_+ \label{reducedbc_2}
\end{align}
and treat the cases $f=0$, $g=0$ separately.  The above boundary conditions are the reduced form of boundary conditions \eqref{bc_1} and \eqref{bc_2} corresponding to $\left.\tau\cdot n\right|_{\Gamma_-}=0$ and $\left.v\right|_{\Gamma_+}=0$.

Additionally, the $\div$ operator is understood now in the weak sense, as the dual operator of $-\grad : H_0^1(\Omega) \rightarrow L^2(\Omega)$, such that $\div f \in \left(H_0^1(\Omega)\right)'$. The normal trace $f\cdot n$ is understood as a limit; smooth functions are dense in $H^1(\Omega)$, and we define $f\cdot n$ as the limit of $f_i\cdot n$, where $f_i \in C^\infty(\Omega)$, $f_i \rightarrow f$.
\textcolor{red}{clearly define what we mean here with the density argument}

>>>>

\author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
\title{$\epsilon$-explicit analysis of DPG for convection-dominated diffusion}
\date{}
\begin{document}

@@

We reduce the adjoint problem to the scalar second order equation
\begin{equation}
- \epsilon \Delta v - \beta \cdot \grad v = g - \epsilon \div f \label{adjoint}
\end{equation}
with boundary conditions
\begin{align}
%\tau \cdot n = 
- \epsilon \grad v \cdot n &=f\cdot n, \quad x\in \Gamma_- \label{reducedbc_1}\\ 
v &= 0, \quad x\in \Gamma_+ \label{reducedbc_2}
\end{align}
and treat the cases $f=0$, $g=0$ separately.  The above boundary conditions are the reduced form of boundary conditions \eqref{bc_1} and \eqref{bc_2} corresponding to $\left.\tau\cdot n\right|_{\Gamma_-}=0$ and $\left.v\right|_{\Gamma_+}=0$. Additionally, the $\div$ operator is understood now in the weak sense, as the dual operator of $-\grad : H_0^1(\Omega) \rightarrow L^2(\Omega)$, such that $\div f \in \left(H_0^1(\Omega)\right)'$.

The appearance of the normal trace $f\cdot n$ necessitates the use of a smooth dense subset of $L^2$.  Formally speaking, we define the adjoint equation \eqref{adjoint} for $f\in C^\infty(\Omega)$.  In doing so, we are allowed to speak of the normal trace $f\cdot n$ on the boundary.  We derive inequalities that are independent of $f\cdot n$ and $\div f$ (quantities that are ill-defined for $L^2(\Omega)$ functions), and note that, since smooth functions are dense in $L^2(\Omega)$, we can take any $L^2$ function to be the limit of $C^\infty(\Omega)$ functions.  Since the inequality holds for all smooth functions and is well-defined for $L^2(\Omega)$ functions, the inequality holds for $L^2(\Omega)$ functions in the limit as well.
